Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/paper.tex
added placeholder perf subsection for DC speedup

>>>>

\subsubsection{Single-Node Scaling for DC Dataset}

\GB{add only speedup plot for entire tree (at least all complete levels) from 1 core to 42 cores}

\begin{itemize}
	\item emphasize we start with a small data set that fits on one node and has only 191 rows
	\item using 1 node (2 sockets), because we are memory bandwidth bound we expect limited speedup but we can save time with parallelism even for this small a data set
\end{itemize}
